---
output: html_document
runtime: shiny
---


```{r setup, include=FALSE, echo= FALSE}
library(shiny)
library(dplyr)
library(ggplot2)
library(tidyr)
require(data.table)
library(tidyverse)
library(DT)
rsconnect::setAccountInfo(name='tianjingcai95',
			  token='886DF70418F9AA110765C3D4A9B2A06D',
			  secret='YULeS4CRLriMmMfpT/F3f8cL04S7iOWs0A+fM/uA')
```



```{r echo= FALSE}
top20_df <- fread('top20.csv')
setnames(top20_df, c('Artist', 'Count', "Median peak", "Mean total weeks", 'Overall sentiment score'))

top20_df <- top20_df[Artist != 'Glee Cast',]

top20_df <- top20_df[1:(nrow(top20_df)-1),] # remove last row of dataframe loaded

# preprocess data
top20_df$`Median peak` = sapply(top20_df$`Median peak`, function(x){round(x, 1)})
top20_df$`Mean total weeks` = sapply(top20_df$`Mean total weeks`, function(x){round(x, 1)})

top20_df$`Overall sentiment score` = sapply(top20_df$`Overall sentiment score`, function(x){round(x, 2)})
```

```{r  echo=FALSE}

# Define UI for application that plots features of movies
ui <- fluidPage(
  titlePanel("Billboard top 20 artists' performance"),
  br(),
  # Sidebar layout with a input and output definitions
  sidebarLayout(

    # Inputs
    sidebarPanel(

      # Select variable for y-axis
      selectInput(inputId = "y",
                  label = "Y-axis:",
                  choices = c("Count" , 
                              "Median peak" , 
                              "Mean total weeks", 
                              "Overall sentiment score" ),
                  selected = "Count"),

      # Select variable for x-axis
      selectInput(inputId = "x",
                  label = "X-axis:",
                  choices = c("Artist"),
                  selected =  "Artist")
    ),

    # Outputs
    mainPanel(
      plotOutput(outputId = "histogram")
    )
  )
)

# Define server function required to create the scatterplot
server <- function(input, output) {

  # Create scatterplot
  output$histogram <- renderPlot({
    ggplot(data = top20_df, aes_string(x = input$x, y = as.name(input$y))) +
      geom_bar(position = "dodge", stat = "identity", aes(fill = input$x)) + coord_flip() + ggtitle("Histogram showing top 20 Billboard artists' performance")
  })




}

# Create the Shiny app object
shinyApp(ui = ui, server = server)
```

#### The R shiny app above provides us an illustration of artists' performance on Billboard evaluated under different metrics. Artists Lil Wayne and Drake have way more songs than other artists nominated on Billboard. On the other hand, our team measure the best rank in history for each of artist's song and we order those ranks and find the median. This metric measures artists overall influence since they began their career. 

#### From the barplot, we could see almost all artists got half their songs achieve top 20 rank on Billboard, which is an amazing achievement. Also, almost all of them have their songs nominated on Billboard more than 5 weeks long. Besides, almost all artists optimistic and delightful information which could be seen from overall sentiment score.

